\LARGE \bf Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence*

### 2015-07-07 Tex_AXYB/paper.tex
All the paper has been revised excpet for some minor changes to be done

\begin{figure}
\centering
\includegraphics[width=3.2in]{fig2.eps}
\caption{
The errors of translation and rotations versus noise covariance exerted to the data $B$".
}
\label{fig3}
\end{figure}

For the numerical experiments in this section, the rotational and translational errors for $X$ and $Y$ are measured as  $Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $Error(t_X) = \parallel (t_{X_{Solved}}-t_{X_{true}})\parallel$, $Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $Error(t_Y) = \parallel (t_{Y_{Solved}}-t_{Y_{true}})\parallel$ respectively.

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig4.eps}
\caption{
The solved $X$ (in blue) and the actual $X$ (in red) in 5 trial simulation with noise covariance 0.01 and shift 2.
}
\label{fig4}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig5.eps}
\caption{
The solved $Y$ (in blue) and the actual $Y$ (in red) in 5 trial simulation with noise covariance 0.01 and shift 2.
}
\label{fig5}
\end{figure}
\end{center}

@@

To test the robustness of the proposed method, noises are exerted to $\{B_i\}$ by $B_i^{noise} = B_i \text{exp}(\mathbf{\widehat{x}}_{noise})$, where each of Lie Algebra element of $\mathbf{x}){noise}$ is Gaussian distribution $N \sim (\mu_{noise},\sigma_{noise})$. In Fig.~\ref{fig3}, As $\sigma_{noise}$ varies from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ are increased as shown in the box-and-whisker plot. There are several outliers not included between the whiskers. The median data can be used as the final solved $X$ and $Y$. Fig.~\ref{fig4} and Fig.~\ref{fig5} show the solved ($X$,$Y$) in blue and actual ($X$,$Y$) in red in coordinate frame.

@@

In this paper, we developed a probabilistic approach to simultaneously obtain  $X$ and $Y$ in $AX=YB$ sensor calibration problem. Without a prior knowledge of the correspondence between $A$ and $B$, in the algorithm the probability theory in Lie group is used to constrain the solution of $X$ and $Y$ to eight candidates. As for the shifted data stream of $A$ and $B$, using the correlation theorem with Euclidean group invariants,the correspondence is recovered to determine the correct solution from eight candidates. In numeric simulation, the method perform well with different data samples.
%\section{Conclusion}
% conference papers do not normally have an appendix

>>>>

\begin{figure}
\centering
\includegraphics[width=3.2in]{fig2.eps}
\caption{
The errors of translation and rotations versus noise covariance exerted to the data $B$.
}
\label{fig3}
\end{figure}

For the numerical experiments in this section, the rotational and translational errors for $X$ and $Y$ are measured as  $Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $Error(t_X) = \parallel t_{X_{Solved}}-t_{X_{true}} \parallel$, $Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $Error(t_Y) = \parallel t_{Y_{Solved}}-t_{Y_{true}} \parallel$ respectively.

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig4.eps}
\caption{
The solved $X$ (in blue) and the actual $X$ (in red) for 5 trials of simulation with noise covariance 0.01 and shift 2.
}
\label{fig4}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig5.eps}
\caption{
The solved $Y$ (in blue) and the actual $Y$ (in red) for 5 trials of simulation with noise covariance 0.01 and shift 2.
}
\label{fig5}
\end{figure}
\end{center}

@@

To test the robustness of the proposed method, noises are exerted to $\{B_i\}$ by the data stream $B_i^{noise} = B_i \text{exp}(\mathbf{\widehat{x}}_{noise})$, where each element of the Lie Algebra $\mathbf{x}_{noise}$ is a Gaussian distribution as $N \sim (\mu_{noise},\sigma_{noise})$. In Fig.~\ref{fig3}, as $\sigma_{noise}$ increments from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ increase as shown in the box-and-whisker plot. There are several outliers outside the whiskers. The median value can be used as the final solved $X$ and $Y$. Fig.~\ref{fig4} and Fig.~\ref{fig5} show the solved ($X$,$Y$)s in blue and the actual ($X$,$Y$) in red in the coordinate frame.

@@

In this paper, we developed a probabilistic approach to simultaneously obtain  $X$ and $Y$ in $AX=YB$ sensor calibration problem. Without a prior knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$, the proposed probabilistic method on Lie group is used to constrain the possible solutions of $X$ and $Y$ to eight pairs of candidates. Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean group invariants,the correspondence is recovered to determine the correct solution among the eight candidates. In the numerical simulation, the method performs well with different sets of data samples.
%\section{Conclusion}
% conference papers do not normally have an appendix
